Integrating Social Visual Analysis and Deployment with RCloud

### 2015-03-30 conclusion.tex
comment on what i think conclusion should be

\stephen{Is this the kind of bad conclusion that contains
a lot of material that should have been explained at the
beginning of the paper to move it along faster and tell
people why they should be interested in the work? What
would be our conclusion?  These capabilties are important,
but they are really hard to program, and adoption is slow
because you're meddling with people's work process and
toolset, which is the heart of their environment and
not some little toy you provide out on the fringes.
Infratsructure is hard.}

@@

Possible next steps are to support cross-language development,
to incorporate richer recommendation techniques, to provide fine-grained
information security, and to improve the usability of the human interface.

>>>>

\stephen{Is this the kind of bad conclusion that contains
a lot of material that should have been explained at the
beginning of the paper to move it along faster and tell
people why they should be interested in the work? What
would be our conclusion?  These capabilties are important,
but they are really hard to program, and adoption is slow
because you're meddling with people's work process and
toolset, which is the heart of their environment and
not some little toy you provide out on the fringes.
Infrastructure is hard.}

\gordon{I think that except for the DevOps slogan, this is redundant and
too dense.  I would replace the first three paragraphs with something
like this:} We designed a prototype environment for exploration, sharing,
presentation, and publishing. The exploration part didn't work out so well,
but people like sharing stuff and integrating web and analysis languages.

@@

Possible next steps are
to incorporate richer recommendation techniques, to provide fine-grained
information security, and to improve the usability of the human interface.
